---
title: 'Activity: Nuclear Reactors'
author: "Sijie Wu"
output:
  html_document:
    df_print: paged
---

```{r}
library(tidyverse)
```

## Scrape the Data 

```{r}
library(rvest)
library(dplyr)

# Scrape the table data from Wikipedia
page <- "https://en.wikipedia.org/wiki/List_of_commercial_nuclear_reactors"
tableList <- page %>%
  read_html() %>%
  html_nodes(css = "table") %>%
  html_table(fill = TRUE)

japan_table <- tableList[[21]]

# View the first few rows to confirm
head(japan_table)
```


## Your turn: In what ways is the table tidy? How is it not tidy? What’s different about it from a tidy table?

It is tidy because each case has its own row, each column represents a single variable. It is not tidy in two ways. First, the date columns (Beginbuilding, Commercialoperation, and Closed) are stored as character strings instead of date objects, which is not optimal for analysis. Second, The column names have inconsistent naming conventions (e.g., Beginbuilding could be more consistent with other date columns).

## Your Turn: Plot Net Generation Capacity vs Construction Date

```{r}
library(ggplot2)
library(lubridate)

# Convert the date column from character to Date type
japan_table <- japan_table %>%
  mutate(begin_building = dmy(`Beginbuilding`))

# Plot Net Generation Capacity vs Construction Date
ggplot(japan_table, aes(x = Beginbuilding, y = `Capacity(MW)`, color = Type)) +
  geom_point() +
  labs(title = "Net Generation Capacity vs Construction Date",
       x = "Construction Date",
       y = "Net Generation Capacity (MW)",
       color = "Reactor Type") +
  theme_minimal()
```


## Your Turn: Scrape & Clean China Data (then merge with Japan)

```{r}
# Scrape the table data from Wikipedia
page <- "https://en.wikipedia.org/wiki/List_of_commercial_nuclear_reactors"
tableList <- page %>%
  read_html() %>%
  html_nodes(css = "table") %>%
  html_table(fill = TRUE)

china_table <- tableList[[10]]

# View the first few rows to confirm
head(china_table)

china_clean <- china_table %>%
  rename(Capacity = `Capacity(MW)`)
  
china_clean <- china_clean %>%
  mutate(
    Capacity = as.numeric(Capacity),
    Beginuilding = dmy(Beginbuilding),
    Commercialoperation = dmy(Commercialoperation)
  )

# Add country column
china_clean <- china_clean %>% mutate(country = "China")

# Check the cleaned data
head(china_clean)

#Clean japan data
japan_clean <- japan_table %>%
  rename(Capacity = `Capacity(MW)`)

japan_clean <- japan_clean %>%
  mutate(
    Capacity = as.numeric(Capacity),
    begin_building = dmy(`Beginbuilding`),
    Commercialoperation = dmy(Commercialoperation),
    country = "Japan"
  )

# join the data
combined_data <- full_join(japan_clean, china_clean, by = c("Plantname", "Type", "Model", "Status", "Capacity", "Commercialoperation","Closed","Beginbuilding","country"))

# Check the joined data
head(combined_data)
```



## Your Turn: Reconstruct Info Graphic of Japan Reactors (or other country of interest)

```{r}
# Plot Net Generation Capacity vs Construction Date
ggplot(combined_data, aes(x = Beginbuilding, y = Capacity, color = Type)) +
  geom_point() +
  labs(title = "Net Generation Capacity vs Construction Date",
       x = "Construction Date",
       y = "Net Generation Capacity (MW)",
       color = "Reactor Type") +
  theme_minimal()
```